New insights into the Weddell Sea ecosystem applying a network approach

### 2022-08-08 Manuscript/Manuscript.Rmd
Started with Results

We obtained the dataset of the Weddell Sea food web from the GlobAL daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig [@Brose2018]. This open access database is a list of predator-prey interactions that contains several highly-resolved food webs, including biological data about the consumer and resource species involved in each trophic interaction (i.e. mean mass). Furthermore, it incorporates information on the interaction itself, such as the dimensionality.
This marine food web compiles all the food web data available for the high Antarctic Weddell Sea collected 
since 1983, and is one of the most highly-resolved marine food webs documented to date. It's noteworthy that it is a 
summary network that ignores seasonal changes [@Jacob2011].

@@

We studied the food web of the Weddell Sea by: a) estimating the strength of each interaction; b) analysing the properties of the species in a network approach; and c) comparing the stability of the food web after performing extinction simulations.

@@

The main equation we used for estimating the interaction strength IS is [@Pawar2012]:

@@

where \vec{\alpha} is the search rate, \vec{x_R} is the density of the resource, and \vec{m_R} and \vec{m_C} are the body mass of the resource and the consumer, respectively.

@@

In order to characterize the species, we considered weighted and unweighted properties (Figure 2). The former is based on the estimation of the interaction strength described in the previous section. The latter is related to properties commonly used in qualitative (presence/absence of interaction) food web studies [@Martinez1991; @Dunne2002; @Borrelli2014]. As weighted property we used the mean interaction strength, meaning the average strength of all species interactions. As unweighted properties we used: a) degree or the total number of trophic interactions taking into account in- and out-interactions (role as predator and prey, respectively); b) trophic level or the position in the food web relative to primary producers/detritus; and c) trophic similarity or the measurement of trophic overlap between species based on shared and unique resources and consumers.

@@

Quasi-Sign Stability (QSS) [@Allesina2008].
After each species extinction, we calculated the QSS for the food web minus one species and compared it with the QSS for the whole network. We statistically analysed such difference applying the Anderson-Darling test [@Scholz1987].

@@

# Content section with R code chunks

```{r, echo = FALSE}
sum <- 1 + 41
```

You should always use `echo = FALSE` on R Markdown code blocks as they
add formatting and styling not desired by Copernicus. The hidden
workflow results in `r sum`.

You can add verbatim code snippets without extra styles by using
```` ``` ```` without additional instructions.

    sum <- 1 + 41

>>>>

We obtained the dataset of the Weddell Sea food web from the GlobAL daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig [@Brose2018]. This open access database is a list of predator-prey interactions that contains several highly-resolved food webs, including biological data about the consumer and resource species involved in each trophic interaction (i.e. mean mass). Furthermore, it incorporates information on the interaction itself, such as the dimensionality.

This marine food web compiles all the food web data available for the high Antarctic Weddell Sea collected since 1983, and is one of the most highly-resolved marine food webs documented to date. It's noteworthy that it is a summary network that ignores seasonal changes [@Jacob2011].

@@

We analysed the food web of the Weddell Sea by: a) estimating the strength of each interaction; b) studying the properties of the species in a network approach; and c) comparing the stability of the food web after performing extinction simulations.

@@

The main equation we used for estimating the interaction strength IS is:

@@

where \vec{\alpha} is the search rate, \vec{x_R} is the density of the resource, and \vec{m_R} and \vec{m_C} are the body mass of the resource and the consumer, respectively [@Pawar2012].

@@

In order to individually characterize the species of the food web, we considered weighted and unweighted properties (Figure 2). The former is based on the estimation of the interaction strength described in the previous section. The latter is related to properties commonly used in qualitative (presence/absence of interaction) food web studies [@Martinez1991; @Dunne2002; @Borrelli2014]. As weighted property we took into account the mean interaction strength, meaning the average strength of all interactions. As unweighted properties we used: a) degree or the total number of trophic interactions, taking into account in- and out-interactions (role as predator and prey, respectively); b) trophic level or the position in the food web relative to primary producers/detritus; and c) trophic similarity or the trophic overlap between species based on shared and unique resources and consumers.

Formulas used to obtain the mentioned species properties are described in Appendix A1.

@@

Finally, we run extinction simulations and estimated its impact on the stability of the network. For this, we calculated a stability index called Quasi-Sign Stability (QSS), which is the proportion of stable networks using randomized Jacobians and keeping the predator-prey sign structure fixed [@Allesina2008]. With the aim of analysing the effect of each species on the food web's stability, we deleted one species at a time, so the network size was reduced by one. After each species extinction, we calculated the QSS for the food web minus one species (size = 489) and compared it with the QSS for the whole network (size = 490); we performed 1000 simulations for each species. Then we statistically analysed such difference with an Anderson-Darling test [@Scholz1987].
The formula for the QSS is described in Appendix A2.

All analyses were performed in R software, using packages igraph [@Csardi2005], cheddar [@Hudson2013], and multiweb [@Saravia2019]. The source code and data are available at https://github.com/EcoComplex/WeddellSea.

@@

## Interaction strength

Figure of distribution IS
Model fit

## Species properties and stability

Clustering in 2 groups: high and low IS
Linear regressions btw IS (weighted) and unweighted prop.
Biplots btw QSS difference and weighted and unweighted prop.

### 2022-08-08 Manuscript/Manuscript.tex
Started with Results

We obtained the dataset of the Weddell Sea food web from the GlobAL
daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of
the German Centre for Integrative Biodiversity Research (iDiv)
Halle-Jena-Leipzig \citep{Brose2018}. This open access database is a
list of predator-prey interactions that contains several highly-resolved
food webs, including biological data about the consumer and resource
species involved in each trophic interaction (i.e.~mean mass).
Furthermore, it incorporates information on the interaction itself, such
as the dimensionality. This marine food web compiles all the food web
data available for the high Antarctic Weddell Sea collected since 1983,
and is one of the most highly-resolved marine food webs documented to
date. It's noteworthy that it is a summary network that ignores seasonal
changes \citep{Jacob2011}.

@@

The main equation we used for estimating the interaction strength IS is
\citep{Pawar2012}:

@@

where \vec{\alpha} is the search rate, \vec{x_R} is the density of the
resource, and \vec{m_R} and \vec{m_C} are the body mass of the resource
and the consumer, respectively.

@@

In order to characterize the species, we considered weighted and
unweighted properties (Figure 2). The former is based on the estimation
of the interaction strength described in the previous section. The
latter is related to properties commonly used in qualitative
(presence/absence of interaction) food web studies
\citep{Martinez1991, Dunne2002, Borrelli2014}. As weighted property we
used the mean interaction strength, meaning the average strength of all
species interactions. As unweighted properties we used: a) degree or the
total number of trophic interactions taking into account in- and
out-interactions (role as predator and prey, respectively); b) trophic
level or the position in the food web relative to primary
producers/detritus; and c) trophic similarity or the measurement of
trophic overlap between species based on shared and unique resources and
consumers.

@@

Quasi-Sign Stability (QSS) \citep{Allesina2008}. After each species
extinction, we calculated the QSS for the food web minus one species and
compared it with the QSS for the whole network. We statistically
analysed such difference applying the Anderson-Darling test
\citep{Scholz1987}.

@@

\section{Content section with R code chunks}

You should always use \texttt{echo\ =\ FALSE} on R Markdown code blocks
as they add formatting and styling not desired by Copernicus. The hidden
workflow results in 42.

You can add verbatim code snippets without extra styles by using
\texttt{\textasciigrave{}\textasciigrave{}\textasciigrave{}} without
additional instructions.

\begin{verbatim}
sum <- 1 + 41
\end{verbatim}

@@

\begin{figure}
\includegraphics[width=8.3cm]{Nikolaus_Kopernikus} \caption{one column figure}\label{fig:unnamed-chunk-5}
\end{figure}

@@

\begin{figure}
\includegraphics[width=12cm]{Nikolaus_Kopernikus} \caption{two column figure}\label{fig:unnamed-chunk-6}
\end{figure}

>>>>

We obtained the dataset of the Weddell Sea food web from the GlobAL
daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of
the German Centre for Integrative Biodiversity Research (iDiv)
Halle-Jena-Leipzig \citep{Brose2018}. This open access database is a
list of predator-prey interactions that contains several highly-resolved
food webs, including biological data about the consumer and resource
species involved in each trophic interaction (i.e.~mean mass).
Furthermore, it incorporates information on the interaction itself, such
as the dimensionality.

This marine food web compiles all the food web data available for the
high Antarctic Weddell Sea collected since 1983, and is one of the most
highly-resolved marine food webs documented to date. It's noteworthy
that it is a summary network that ignores seasonal changes
\citep{Jacob2011}.

@@

The main equation we used for estimating the interaction strength IS is:

@@

where \vec{\alpha} is the search rate, \vec{x_R} is the density of the
resource, and \vec{m_R} and \vec{m_C} are the body mass of the resource
and the consumer, respectively \citep{Pawar2012}.

@@

In order to individually characterize the species of the food web, we
considered weighted and unweighted properties (Figure 2). The former is
based on the estimation of the interaction strength described in the
previous section. The latter is related to properties commonly used in
qualitative (presence/absence of interaction) food web studies
\citep{Martinez1991, Dunne2002, Borrelli2014}. As weighted property we
took into account the mean interaction strength, meaning the average
strength of all interactions. As unweighted properties we used: a)
degree or the total number of trophic interactions, taking into account
in- and out-interactions (role as predator and prey, respectively); b)
trophic level or the position in the food web relative to primary
producers/detritus; and c) trophic similarity or the trophic overlap
between species based on shared and unique resources and consumers.

Formulas used to obtain the mentioned species properties are described
in Appendix A1.

@@

Finally, we run extinction simulations and estimated its impact on the
stability of the network. For this, we calculated a stability index
called Quasi-Sign Stability (QSS), which is the proportion of stable
networks using randomized Jacobians and keeping the predator-prey sign
structure fixed \citep{Allesina2008}. With the aim of analysing the
effect of each species on the food web's stability, we deleted one
species at a time, so the network size was reduced by one. After each
species extinction, we calculated the QSS for the food web minus one
species (size = 489) and compared it with the QSS for the whole network
(size = 490); we performed 1000 simulations for each species. Then we
statistically analysed such difference with an Anderson-Darling test
\citep{Scholz1987}. The formula for the QSS is described in Appendix A2.

All analyses were performed in R software, using packages igraph
\citep{Csardi2005}, cheddar \citep{Hudson2013}, and multiweb
\citep{Saravia2019}. The source code and data are available at
https://github.com/EcoComplex/WeddellSea.

@@

\subsection{Interaction strength}

Figure of distribution IS Model fit

\subsection{Species properties and stability}

Clustering in 2 groups: high and low IS Linear regressions btw IS
(weighted) and unweighted prop. Biplots btw QSS difference and weighted
and unweighted prop.

@@

\begin{figure}
\includegraphics[width=8.3cm]{Nikolaus_Kopernikus} \caption{one column figure}\label{fig:unnamed-chunk-4}
\end{figure}

@@

\begin{figure}
\includegraphics[width=12cm]{Nikolaus_Kopernikus} \caption{two column figure}\label{fig:unnamed-chunk-5}
\end{figure}
